Spatial Reasoning and Statistical Graphics

### 2014-10-20 Paper/Draft1/TestingVisualAptitude.Rnw
Figure tweaks.
Transition text/comments and new paragraph heading.

\begin{figure}[htbp]\centering
\includegraphics[width=.9\textwidth]{lineup}
\caption[Sample Lineup]{A sample lineup. Participants are instructed to choose the plot which appears most different from the others. In this lineup, plot 13 is the target. }\label{fig:lineup}
\end{figure}

@@

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. About one-half of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, education, and liberal arts. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative of the university as a whole; ISU graduates are about 20\% engineering, 16\% business, and 11\% agriculture students, however, these numbers are for completed degrees, not current majors. 
\comment{Heike, can you get better enrollment numbers for current students? My guess is there are more people enrolled in engineering than actually graduate :). }
% \comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}

The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students). We compare Iowa State students' unscaled scores in table \ref{tab:scorecomparison}, adjusting data from other populations to account for subpopulation structure and test length.

>>>>

\begin{figure}\centering
\includegraphics[width=.8\textwidth]{lineup}
\caption[Sample Lineup]{A sample lineup. Participants are instructed to choose the plot which appears most different from the others. In this lineup, plot 13 is the target. }\label{fig:lineup}
\end{figure}

@@

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. About one-half of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, education, and liberal arts. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative of the university as a whole; ISU graduates are about 20\% engineering, 16\% business, and 11\% agriculture students, however, these numbers are for completed degrees, not current majors. 
\comment{Heike, can you get better enrollment numbers for current students? My guess is there are more people enrolled in engineering than actually graduate :). }

\newtext{The testing was conducted by two research assistants; the first tested 18 participants, the second tested 20 participants. A comparison of results from each researcher is available in appendix \ref{app:ratests}. }
% \comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}

\paragraph{Comparison of Spatial Tests with Previously Validated Results}
The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students). We compare Iowa State students' unscaled scores in table \ref{tab:scorecomparison}, adjusting data from other populations to account for subpopulation structure and test length.
